Current Affairs: Utilizing Oxford Nanopore Sequencing Data to Detect Non-Canonical DNA Structures

### 2024-01-29 jan30meeting_pres1/may30ccgmeeting.tex
updates

	%%% EXPLAIN NSSE SURVEY A BIT
	%%% WHEN YOU TALK MENTION THAT THEY DID THIS SURVEY AFTER PLAYING THE GAME IN CLASS
	\begin{frame}{Results of the Model}

		\textbf{\color{blue}Pan-Cancer Analysis:} Analysis of multiple types of cancer simultaneously, aims to identify commonalities shared across different types

		\textbf{\color{blue}Cancer-Specific Analysis:} Analysis of individual cancer types to better understand the variation within a specific cancer type \vspace{1cm}

		\begin{itemize}
			\item Pan-cancer analyses may overlook cancer-specific differences
			\item Availability of datasets for all cancer types varies, this may limit statistical power of pan-cancer analyses
		\end{itemize}

@@

	\begin{frame}{The Objective}
		Human sex differences are mainly caused by;
		\begin{enumerate}
			\item Gonadal hormone secretions
			\item Genes located on the sex chromosomes (X and Y) \newline
		\end{enumerate}
	This leads to differences in the frequency of certain cancer types and the efficacy of treatments in males and females
	\end{frame}

>>>>

	%%% EXPLAIN NSSE SURVEY A BIT
	%%% WHEN YOU TALK MENTION THAT THEY DID THIS SURVEY AFTER PLAYING THE GAME IN CLASS
	\begin{frame}{Model Performance}
		At an FDR control level $\alpha = 0.2$, SVM and GoFAE-DND generated the most novelties, with GoFAE-DND yielding the most predictions for all non-B types besides G4
		\begin{center}
			\vspace{-1cm}
			\includegraphics[width=12cm, height=8cm]{model_performance_gofae.png}
		\end{center}

@@

	\begin{frame}{The Objective}
		Given the dramatic increase in genome-scale data produced using ONT platforms, and the relevance of non-B structures in human cancers; \newline
		\begin{enumerate}
			\item Utilize the model to analyze nanopore samples from the human pangenome reference consortium (HPRC)
			\item Eventually improve the model, with an emphasis on the detection of G4 quadruplexes - Linking methylation, gene expression profiles which are available for HPRC samples\newline
		\end{enumerate}
	\end{frame}
